\documentclass{article}%
\usepackage[T1]{fontenc}%
\usepackage[utf8]{inputenc}%
\usepackage{lmodern}%
\usepackage{textcomp}%
\usepackage{lastpage}%
\usepackage{tabularx}%
%

\usepackage{latexsym}
\usepackage[a4paper, total={6in, 8in}]{geometry}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{xcolor}
\usepackage{fontawesome5}
\input{glyphtounicode}
% \include{Skills}
% -------------------- FONT OPTIONS --------------------
% sans-serif
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% serif
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-1in} % Default was -.5in
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Subsection formatting
\titleformat{\subsection}{
  \vspace{-4pt}\scshape\raggedright\large
}{\hspace{-.15in}}{0em}{}[\color{black}\vspace{-8pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%
\usepackage{fontawesome5} \usepackage{titlesec} \usepackage{xcolor} % Ensures color functionality%
%
\begin{document}%
\normalsize%
\vspace{-10mm}%

    \begin{description}
    \item 
        \begin{center}
            \textbf{\Huge \scshape Muhammad Talha} \\ \vspace{8pt}
            \small 
            \faIcon{github}
            {\underline{/Wolfbiter771}} $  $
            \faIcon{linkedin}
            {\underline{in/tjbravo}} $  $
            \faIcon{envelope}
            {\underline{talha.j771@gmail.com}} $  $
            \faIcon{phone}
            {\underline{2149093357}}
        \end{center}
    \end{description}
    %
\section*{Education}%
\label{sec:Education}%

%
\subsection*{}%
\label{subsec:}%
\vspace{-4mm}%
\noindent%
\textbf{Habib University}%
\hfill%
2020 - 2024%
 \newline%
%
\textit{Bachelors of Computer Science}

%
\subsection*{}%
\label{subsec:}%
\vspace{-4mm}%
\noindent%
\textbf{Alpha College}%
\hfill%
2018 - 2020%
 \newline%
%
\textit{Advanced Level GCSE}

%
\section{Skills}%
\label{sec:Skills}%
\begin{description}%
\item[]%
Languages: Python, JavaScript, C++, SQL%
\item[]%
Tools: Docker, PostgreSQL, Git, AWS, Kubernetes%
\end{description}

%
\section*{Experience}%
\label{sec:Experience}%

%
\subsection*{}%
\label{subsec:}%
\vspace{-4mm}%
\begin{tabularx}{\textwidth}{cXr}%
\textbf{Acme Corp |}&\textit{Full Stack Engineer (NodeJs/Express/React/Typescript)}&January 2022 — Current\\%
\end{tabularx}%
\begin{itemize}%
\item%
Developed scalable web applications%
\item%
Collaborated with cross{-}functional teams%
\item%
Implemented RESTful APIs%
\end{itemize}

%
\subsection*{}%
\label{subsec:}%
\vspace{-4mm}%
\begin{tabularx}{\textwidth}{cXr}%
\textbf{Tech Innovators Inc. |}&\textit{Software Engineer (Python/Django/PostgreSQL/Docker)}&June 2020 — December 2021\\%
\end{tabularx}%
\begin{itemize}%
\item%
Designed and developed RESTful APIs using Django%
\item%
Optimized database queries for better performance%
\item%
Deployed applications using Docker and Kubernetes%
\end{itemize}

%
\section*{Projects}%
\label{sec:Projects}%

%
\subsection*{}%
\label{subsec:}%
\vspace{-4mm}%
\begin{tabularx}{\textwidth}{cXr}%
\textbf{Yohsin Connect |}&\textit{ (Python/LangChain/FAISS/PyTorch/TensorFlow)}&2024 — Current\\%
\end{tabularx}%
\begin{itemize}%
\item%
Developed a Retrieval Augmented Generation (RAG) chatbot to provide instant responses to inquiries from prospective students at Habib University.%
\item%
Integrated advanced LLM models using TensorFlow and PyTorch to understand and generate human{-}like responses.%
\item%
Utilized LangChain for streamlined implementation of chat functionalities and FAISS for efficient information retrieval from a large vector database/store of university{-}related documents.%
\end{itemize}

%
\subsection*{}%
\label{subsec:}%
\vspace{-4mm}%
\begin{tabularx}{\textwidth}{cXr}%
\textbf{Personal Home Lab and Smart Home Setup |}&\textit{ (YAML/Python/Docker)}&Ongoing — Current\\%
\end{tabularx}%
\begin{itemize}%
\item%
Configured diverse services: Jellyfin, Home Assistant, Transmission Daemon with public access.%
\item%
Managed Docker containers for efficient deployment.%
\end{itemize}

%
\subsection*{}%
\label{subsec:}%
\vspace{-4mm}%
\begin{tabularx}{\textwidth}{cXr}%
\textbf{BomberMan Clone |}&\textit{ (C++/SDL2/Sprite Animations/Polymorphism)}&December 2021 — Current\\%
\end{tabularx}%
\begin{itemize}%
\item%
Recreated the famous Bomberman game in C++ using SDL2, including sprite animations and custom game mechanics.%
\item%
Implemented OOP design patterns and polymorphism.%
\end{itemize}

%
\end{document}